---
title: "group_15_ca_ej"
author: "Andrea Cornelius"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# Attach packages
library(tidyverse)
library(janitor)
library(here)
```

```{r}
# Read in data
ces <- read_csv(here("data", "ces3demographics.csv")) %>%
  clean_names()
```

```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
         geom_hex() +
  labs(x = "Percentage White",
       y = "CES 3.0 Score") +
  scale_fill_gradient(low = "lightblue", high = "red") +
  theme_minimal()
```

**Figure 1: CES 3.0 scores and percentage white population**

Generally speaking CES 3.0 Score is decreasing with increasing white population percentage (inversely correlated). Trend is roughly linear, however further analysis is required for conclusive determination.

Data Source: CalEnviroScreen 3.0. California Office of Environmental Health Hazard Assessment (2018). California Environmental Protection Agency (CalEPA). https://oehha.ca.gov/media/downloads/calenviroscreen/document-calenviroscreen/raceageces3analysis.pdf
